

Firstly, visit \url{https://ai.googleblog.com/2020/02/ml-fairness-gym-tool-for-exploring-long.html} and  \url{https://github.com/google/ml-fairness-gym} and start working on one of the dynamic environments there. In particular, I recommend you study the credit score environment. Using the environments requires the open-AI gym \url{https://gym.openai.com/}

As a first step, you should place the variables into the following categories:
\begin{itemize}
\item Features $x_t$, that e.g. describe the patient $t$ in a medical database
\item Actions $a_t$ that describe whatever intervention has been taken, if applicable. There is always at least one action, even if not included in the dataset. E.g. for a diagnostic database, the action would be 'perform the diagnosis'.
\item Outcomes $y_t$ that describe what happens after the action has been taken.
\item The utility function $U$ that describes what  $y_t$ that describe what happens after the action has been taken.
\end{itemize}


\textbf{Simulation selection and analysis (Nov 6)} Here you should describe the simulation, and analyse the data it produces with a simple, default policy for making decisions. You should in particular try to
\begin{itemize}
\item Try out a simple, random agent
\item Identify causal relations
\item Identify sensitive variables and possible fairness metrics.
\item Point out privacy issues
\item Discuss the utility function
\end{itemize}

\textbf{Improved policies (Nov 20)} Here you should come up with an algorithm that produces improved policies in some sense. Possible things to do include:
\begin{itemize}
\item Define a parametric or non-parametric policy for making decisions.
\item Perform an analysis of this policy in terms of performance.
\item Start a preliminary analysis on fairness and privacy of that policy.
\end{itemize}


\textbf{Final report (Dec 6)} In the final report, make sure to communicate everything related to reproducibility, fairness and privacy of your methodology and the policy you have derived. The final report should include an improved version of your policy and you should concisely discuss 
\begin{itemize}
\item Reproducibility
\item Fairness
\item Privacy
\end{itemize}







%%% Local Variables:
%%% mode: latex
%%% TeX-master: "open-ended-project"
%%% End:
